\psalmverse{Magníficat \grecross\ * ánima méa Dóminum.}{My soul doth magnify the Lord.}
\psalmverse{Et exsultávit spíritus méus * in Déo salutári méo.}{And my spirit hath rejoiced in God my Saviour.}
\psalmverse{Quia respéxit humilitátem ancíllae súæ: * ecce enim ex hoc beátam me dícent ómnes generatiónes.}{Because he hath regarded the humility of his handmaid: for behold from henceforth all generations shall call me blessed.}
\psalmverse{Quia fécit míhi mágna qui pótens est: * et sánctum nómen éjus.}{Because he that is mighty hath done great things to me: and holy is his name.}
\psalmverse{Et misericórdia éjus a progénie in progénies * timéntibus éum.}{And his mercy is from generation unto generations, to them that fear him.}
\psalmverse{Fécit poténtiam in bráchio súo: * dispérsit supérbos ménte córdis súi.}{He hath shewed might in his arm: he hath scattered the proud in the conceit of their heart.}
\psalmverse{Depósuit poténtes de séde, * et exaltávit húmiles.}{He hath put down the mighty from their seat and hath exalted the humble.}
\psalmverse{Esuriéntes implévit bónis: * et dívites dimísit inánes.}{He hath filled the hungry with good things: and the rich he hath sent empty away.}
\psalmverse{Suscépit Israel púerum súum, * recordátus misericórdiæ súæ.}{He hath received Israel his servant, being mindful of his mercy.}
\psalmverse{Sicut locútus est ad pátres nóstros, * Abraham et sémini éjus in saécula.}{As he spoke to our fathers: to Abraham and to his seed for ever.}
\psalmverse{Glória Pátri, et Fílio,~* et Spirítui Sáncto.}{Glory be to the Father and to the Son, and to the Holy Ghost.}
\psalmverselast{Sicut érat in princípio, et núnc, et sémper,~* et in sǽcula sæculórum. Amen.}{As it was in the beginning, is now, and ever shall be, world without end.  Amen.}
