%\psalmverse{[Deus, in nómine tuo sálvum me fac, * et in virtúte tua júdica me.]}{Save me, O God, by thy name, and judge me in thy strength.}
\psalmverse{Deus, exáudi orati\textbf{ó}nem \textbf{me}am; * áuribus pércipe verba \textbf{o}ris \textbf{me}i.}{O God, hear my prayer: give ear to the words of my mouth.}
\psalmverse{Quóniam aliéni insurrexérunt advérsum me, \dag\ et fortes quaesiérunt \textbf{á}nimam \textbf{me}am: * et non proposuérunt Deum ante con\textbf{spé}ctum \textbf{su}um.}{For strangers have risen up against me; and the mighty have sought after my soul: and they have not set God before their eyes.}
\psalmverse{Ecce enim Deus \textbf{ád}ju\textbf{vat} me, * et Dóminus suscéptor est \textbf{á}nimae \textbf{me}ae.}{For behold God is my helper: and the Lord is the protector of my soul.}
\psalmverse{Avérte mala ini\textbf{mí}cis \textbf{me}is; * et in veritáte tua dis\textbf{pér}de \textbf{il}los.}{Turn back the evils upon my enemies; and cut them off in thy truth.}
\psalmverse{Voluntárie sacrifi\textbf{cá}bo \textbf{ti}bi, * et confitébor nómini tuo, Dómine, \textbf{quó}\-niam \textbf{bo}num est.}{I will freely sacrifice to thee, and will give praise, O God, to thy name: because it is good:}
\psalmverse{Quóniam ex omni tribulatióne e\textbf{ri}\-pu\-\textbf{í}\-sti me, * et super inimícos meos despéxit \textbf{ó}culus \textbf{me}us.}{For thou hast delivered me out of all trouble: and my eye hath looked down upon my enemies.}
\psalmverse{Glória \textbf{Pa}tri et \textbf{Fí}lio * et Spi\textbf{rí}tui \textbf{San}cto.}{Glory be to the Father and to the Son, and to the Holy Ghost.}
\psalmverselast{Sicut erat in princípio, et \textbf{nunc} et \textbf{sem}per * et in sáecula saecu\textbf{ló}rum. \textbf{A}men.}{As it was in the beginning, is now, and ever shall be, world without end.  Amen.}

