\psalmverse{[Saepe expugnaverunt me a juventute mea * dicat nunc Israel.]}{Often have they fought against me from my youth, let Israel now say.}
\psalmverse{Sæpe expugnavérunt me a juven\textit{túte} \textbf{me}a~:~* étenim non potuérunt mihi.}{Often have they fought against me from my youth: but they could not prevail over me.}
\psalmverse{Supra dorsum meum fabricavérunt \textit{pecca}\textbf{tó}res~:~* prolongavérunt iniquitátem suam.}{The wicked have wrought upon my back: they have lengthened their iniquity.}
\psalmverse{Dóminus justus concídit cervíces \textit{pecca}\textbf{tó}rum~:~* confundántur et convertántur retrórsum omnes, qui odérunt Sion.}{The Lord who is just will cut the necks of sinners: Let them all be confounded and turned back that hate Sion.}
\psalmverse{Fiant sicut fœ\textit{num} \textit{te}\textbf{ctó}rum~:~* quod priúsquam evellátur exáruit~:}{Let them be as grass upon the tops of houses: which withereth before it be plucked up:}
\psalmverse{De quo non implévit manum su\textit{am} \textit{qui} \textbf{me}tit~:~* et sinum suum qui manípulos cólligit.}{Who with the mower filleth not his hand: nor he that gathereth
sheaves his bosom.}
\psalmverse{Et non dixérunt qui præteríbant~: Benedíctio Dó\textit{mini} \textbf{su}per vos~:~* benedíximus vobis in nómine Dómini.}{And they that passed by have not said: The blessing of the Lord be upon you: we have blessed you in the name of the Lord.}
\psalmverse{Glória Pá\textit{tri}, \textit{et} \textbf{Fí}lio,~* et Spirítui Sáncto.}{Glory be to the Father and to the Son, and to the Holy Ghost.}
\psalmverselast{Sicut érat in princípio, et \textit{núnc}, \textit{et} \textbf{sém}per,~* et in sǽcula sæculórum. Amen.}{As it was in the beginning, is now, and ever shall be, world without end.  Amen.}
