\documentclass[a5paper,12pt,twoside,openany]{memoir}
\usepackage[british,latin]{babel}
\usepackage{fontspec}
\defaultfontfeatures{Ligatures=TeX}
\setmainfont[Numbers=OldStyle]{Linux Libertine O}
%\setmainfont{EB Garamond}
\newfontfamily{\anavio}{Linux Libertine O}
%\newfontfamily{\vectis}{Vectis}
\newfontface{\vectis}{Vectis Bold}
\newfontface{\versicles}{Versiculum}
\newfontface{\inglesh}{Worstveld Sling}
%\usepackage{parallel}
%\usepackage{lettrine}
\newfontface{\cruci}{Juuji}
\usepackage{gregoriotex}
%\settrimmedsize{9in}{6in}{*}
\setlength{\trimtop}{0pt}
\setlength{\trimedge}{0pt}
%\addtolength{\trimedge}{-\paperwidth}
\settypeblocksize{170mm}{116mm}{*} % Was 101mm in a5
\setulmargins{*}{*}{1.4}
\setlrmargins{*}{*}{1.2}
\setheadfoot{\onelineskip}{2\onelineskip}
\setheaderspaces{*}{.8\onelineskip}{*}
\checkandfixthelayout

\tolerance=1000
\pretolerance=800

\setlength{\parskip}{6pt plus 2pt minus 1pt}
\setlength{\parindent}{0pt}
\setlength{\stanzaskip}{6pt plus 2pt minus 1pt}

\newlength{\gcolwidth}
\setlength{\gcolwidth}{0.48\textwidth}
\newlength{\lcolwidth}
\setlength{\lcolwidth}{0.53\textwidth}
\newlength{\vcolwidth}
\setlength{\vcolwidth}{0.43\textwidth}

\renewcommand\gretranslationformat[1]{{\inglesh \fontsize{14}{10}\selectfont #1}}

\setgrefactor{16}


\newcounter{versecount}
\setcounter{versecount}{0}

\def\latin#1{\ifnum \value{versecount}>0 \stepcounter{versecount} \theversecount .~\fi\selectlanguage{latin}#1\selectlanguage{british}\\}
\def\vern#1{{\inglesh \fontsize{14}{11}\selectfont #1}\par}

\def\startParallel{}
\def\stopParallel{}

\setlength{\parskip}{3pt plus 2pt minus 1pt}

\def\firstlatin#1#2#3{%
\latin{%
\noindent\begin{minipage}[t]{\ParallelLWidth}%
\lettrine{#1}{#2}#3\strut%\vspace{0.9mm}\vspace{0.13cm}%
\end{minipage}%
}%
%\vspace{-0.2cm}%
}

\def\firstvern#1#2#3{%
\vern{%
\noindent\begin{minipage}[t]{\ParallelRWidth}%
\lettrine{#1}{#2}\gretranslationformat{#3}\strut%\vspace{0.9mm}\vspace{0.13cm}%
\end{minipage}%
}%\vspace{-0.2cm}%
}

\newcommand\maltese{{\tiny \cruci V}\ }

\renewcommand\Vbar{\makebox[1em][l]{\versicles v}}
\renewcommand\Rbar{\makebox[1em][l]{\versicles r}}

\let\oldtextbf\textbf


\newcommand\rubrics[1]{\textit{#1}}
\newcommand\bibleref[2]{\oldtextbf{#1} \hfill \textit{#2}}
\newcommand\psalm[1]{~ \hfill \oldtextbf{Psalm #1.} \hfill ~}

\title{Ad Sextam}

%\chapterstyle{thatcher}
%\chapterstyle{dowding}
\chapterstyle{dash}

\begin{document}


\nouppercaseheads
\pagestyle{myheadings}

\makeevenhead{myheadings}{\thepage}{\textsc{\leftmark}}{}
\makeoddhead{myheadings}{}{\textsc{\rightmark}}{\thepage}

\createmark{section}{right}{nonumber}{\sectionname}{}
\createmark{chapter}{left}{nonumber}{\chaptername}{}

\setcounter{secnumdepth}{0}


\maketitle

\tableofcontents

\chapter{The beginning}
\label{beginning}

\bigskip

\rubrics{Making the sign of the cross:}

\includescore{deusinadjengl}

\bigskip

%\Vbar.\ O God, come to my assistance.

%\Rbar.\ O Lord, make haste to help me.

%Glory be\ldots

%\newpage

\section{Hymn}

\gresetfirstlineaboveinitial{2}{2}
\includescore{mementolit}


%\newpage


\section{Psalmody}

\rubrics{Usually sit at the first asterisk for each psalm, rise at the asterisk for the last verse of the psalm ready to bow for the \emph{Gloria Patri}, upright for \emph{Sicut erat}, then remain standing until the first asterisk of the next psalm.}

\rubrics{The antiphon varies for Advent (see page \pageref{missusest}) and Christmas (see page \pageref{oadmirabile}.) Otherwise as below.}

\subsection{Per Annum.}

\gresetfirstlineaboveinitial{4A}{4A}
\includescore{gabc/an--in_odorem--solesmes}

\subsubsection{Psalm 122}

\includescore{gabc/ps122init}

\setcounter{versecount}{1}
\input psalms/122-4A

\subsubsection{Psalm 123}

\includescore{gabc/ps123init}

\setcounter{versecount}{1}
\input psalms/123-4A

\subsubsection{Psalm 124}

\includescore{gabc/ps124init}

\setcounter{versecount}{1}
\input psalms/124-4A

\includescore{gabc/an--in--noincipit}

\setcounter{versecount}{0}



\section{Chapter}

\includescore{etradicavi}

\latin{\Vbar Benedicta tu in mulieribus.}\vern{Blessed art thou among women.}
\latin{\Rbar Et benedictus fructus ventris tui.}\vern{And blessed is the fruit of thy womb.}

\section{Collect}

%\startParallel
\latin{\Vbar Dómine, exaudi oratiónem meam.}
\vern{O Lord, hear my prayer.}
\latin{\Rbar Et clamor meus ad te véniat.}
\vern{And let my cry come unto Thee.}
\latin{Orémus.}
\vern{Let us pray.}
\latin{Conc\'ede, mis\'ericors Deus, fragilit\'ati nostr\ae \ pr\ae \-s\'\i \-dium : \dag \ 
ut qui sanct\ae \ Dei Genitr\'\i cis mem\'oriam \'agimus, * 
intercessi\'onis ejus aux\'\i lio, a nostris iniqui\-t\'a\-tibus resurg\'amus.
Per eúmdem Dóminum nostrum Iesum Christum Filium tuum, qui tecum vivit et regnat in unitáte Spíritus Sancti, Deus, per ómnia sǽcula sæculórum.}
%Per e\'umdem Christum D\'ominum nostrum.}
\vern{We beseech thee, O Lord, mercifully to assist our infirmity: that like as we do now commemorate Blessed Mary Ever-Virgin, Mother of God; so by the help of her intercession we may die to our former sins and rise again to newness of life. %Through the same Christ our Lord.}
Through the same Jesus Christ, thy Son, Our Lord, Who liveth and reigneth with thee in the unity of the Holy Ghost, God, world without end.}
\latin{\Rbar Amen.}
\vern{Amen.}
\latin{\Vbar Dómine, exaudi oratiónem meam.}
\vern{O Lord, hear my prayer.}
\latin{\Rbar Et clamor meus ad te véniat.}
\vern{And let my cry come unto Thee.}
\latin{\Vbar Benedicámus Dómino.}
\vern{Let us bless the Lord.}
\latin{\Rbar Deo grátias.}
\vern{Thanks be to God.}
\latin{\Vbar Fidélium ánimae per misericórdiam Dei requiéscant in pace.}\vern{May the souls of the faithful departed through the mercy of God rest in peace.}
\latin{\Rbar Amen.}
\vern{Amen.}
%\stopParallel



\end{document}
