\latin{Cum exsúrgerent hó\textit{mi}\textit{nes} \textbf{in} nos,~* forte vi\textit{vos} \textit{de}\textit{glu}\textbf{tís}sent nos~:}\vern{When men rose up against us, perhaps they had swallowed us up alive.}
\latin{Cum irascerétur furor e\textit{ó}\textit{rum} \textbf{in} nos,~* fórsitan aqua \textit{ab}\textit{sor}\textit{bu}\textbf{ís}set nos.}\vern{When their fury was enkindled against us, perhaps the waters had swallowed us up.}
\latin{Torréntem pertransívit á\textit{ni}\textit{ma} \textbf{no}stra~:~* fórsitan pertransísset ánima nostra aquam \textit{in}\textit{to}\textit{le}\textbf{rá}bilem.}\vern{Our soul hath passed through a torrent: perhaps our soul had passed through a water insupportable.}
\latin{Bene\textit{dí}\textit{ctus} \textbf{Dó}minus~* qui non dedit nos, in captiónem dén\textit{ti}\textit{bus} \textit{e}\textbf{ó}rum.}\vern{Blessed be the Lord, who hath not given us to be a prey to their teeth.}
\latin{Anima nostra sicut pas\textit{ser} \textit{e}\textbf{rép}ta est~* de lá\textit{que}\textit{o} \textit{ve}\textbf{nán}tium.}\vern{Our soul hath been delivered as a sparrow out of the snare of the fowlers.}
\latin{Láque\textit{us} \textit{con}\textbf{trí}tus est,~* et nos li\textit{be}\textit{rá}\textit{ti} \textbf{su}mus.}\vern{The snare is broken, and we are delivered.}
\latin{Adjutórium nostrum in nó\textit{mi}\textit{ne} \textbf{Dó}mini,~* qui fecit \textit{cæ}\textit{lum} \textit{et} \textbf{ter}ram.}\vern{Our help is in the name of the Lord, who made heaven and earth.}
\latin{Glória Pá\textit{tri}, \textit{et} \textbf{Fí}lio,~* et Spi\textit{rí}\textit{tu}\textit{i} \textbf{Sán}cto.}\vern{Glory be to the Father and to the Son, and to the Holy Ghost.}
\latin{Sicut érat in princípio, et \textit{núnc}, \textit{et} \textbf{sém}per,~* et in sǽcula sæ\textit{cu}\textit{ló}\textit{rum}. \textbf{A}men.}\vern{As it was in the beginning, is now, and ever shall be, world without end.  Amen.}
