\latin{Montes in circúitu ejus~:~† et Dóminus in circúitu pó\textit{pu}\textit{li} \textbf{su}i,~* ex hoc nunc et \textit{us}\textit{que} \textit{in} \textbf{sǽ}culum.}\vern{Mountains are round about it: so the Lord is round about his people from henceforth now and for ever.}
\latin{Quia non relínquet Dóminus virgam peccatórum super sor\textit{tem} \textit{ju}\textbf{stó}rum~:~* ut non exténdant justi ad iniquitá\textit{tem} \textit{ma}\textit{nus} \textbf{su}as.}\vern{For the Lord will not leave the rod of sinners upon the lot of the just: that the just may not stretch forth their hands to iniquity.}
\latin{Bénefac, Dó\textit{mi}\textit{ne}, \textbf{bo}nis,~* \textit{et} \textit{re}\textit{ctis} \textbf{cor}de.}\vern{Do good, O Lord, to those that are good, and to the upright of heart.}
\latin{Declinántes autem in obligatiónes addúcet Dóminus cum operántibus in\textit{i}\textit{qui}\textbf{tá}tem~:~* \textit{pax} \textit{su}\textit{per} \textbf{Is}raël.}\vern{But such as turn aside into bonds, the Lord shall lead out with the workers of iniquity: peace upon Israel.}
\latin{Glória Pá\textit{tri}, \textit{et} \textbf{Fí}lio,~* et Spi\textit{rí}\textit{tu}\textit{i} \textbf{Sán}cto.}\vern{Glory be to the Father and to the Son, and to the Holy Ghost.}
\latin{Sicut érat in princípio, et \textit{núnc}, \textit{et} \textbf{sém}per,~* et in sǽcula sæ\textit{cu}\textit{ló}\textit{rum}. \textbf{A}men.}\vern{As it was in the beginning, is now, and ever shall be, world without end.  Amen.}
